Title Goes Here

### 2020-02-24 paper/paper.tex
formatting
Typo in equation
Paper equations now reflect modified tail recursion transformation with increased intermediate type-safety
Added note about the tail recursion transformation being independent of the rest of the EDSL transformations and 'E' type
Handle lambdas properly (including those generated from tail rec transformation)
Section on the structure of the paper

@@

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &:= \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter $A\expr{\lambda \ttt{x} \rarr \ttt{case s of $T_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}}$)}}$} & \text{if \ttt{f} occurs in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}\\
\end{align*}

\begin{align*}
  T_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \\
    &:=
      \begin{cases}
        \ttt{\{ K x0 ... xN $\rarr$ body}[\ttt{f} \mapsto \ttt{Step}]\ttt{; }T_{\ttt{f}}\expr{\ttt{\{ ... \}}}\ttt{ \}} & \text{if \ttt{f} occurs in \ttt{body}}\\
        \ttt{\{ K x0 ... xN $\rarr$ Done body; ... \}} & \text{otherwise}
      \end{cases}\\
  T_f&\expr{\ttt{\{ \}}} := \ttt{\{ \}}\\
\end{align*}
\begin{align*}
  &C^{*}\expr{\ttt{x}} :=
    \begin{cases}
      \ttt{x} & \text{if \ttt{x} has no marked subexpressions}\\
      C^{*}\expr{C\expr{\ttt{externalize y}}} & \text{if \ttt{externalize y} is the first marked subexpression of \ttt{x}}\\
    \end{cases}\\
\end{align*}
\begin{align*}
  &C\expr{\ttt{externalize (runIter x)}} := \ttt{TailRec $M\expr{\ttt{x}}$}\\
  &C\expr{\ttt{externalize (x + y)}} := \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} := \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} := \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} = \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} := \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} := \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} := \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} := \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} :=
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}

@@

\section{Citations and Bibliographies}

>>>>

\subsection{Structure of the Paper}

\begin{itemize}
  \item In section 3, an EDSL representation of pattern matching will be
    introduced.
  \item Sections 4 and 5 will discuss techniques for representing tail recursion
    and lambdas (respectively) in an EDSL. The tail recursion transformation
    does not depend on the rest of the EDSL and can be used separately from it.
  \item Section 7 describes the general control flow and specific syntactic
    transformations of the Core plugin.
\end{itemize}

@@

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &:= \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}\\
\end{align*}

\begin{align*}
  T_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \\
    &:=
      \begin{cases}
        \ttt{\{ K x0 ... xN $\rarr$ body}[\ttt{f} \mapsto \ttt{Step}]\ttt{; }T_{\ttt{f}}\expr{\ttt{\{ ... \}}}\ttt{ \}} & \text{if \ttt{f} occurs in \ttt{body}}\\
        \ttt{\{ K x0 ... xN $\rarr$ Done body; ... \}} & \text{otherwise}
      \end{cases}\\
  T_{\ttt{f}}&\expr{\ttt{\{ \}}} := \ttt{\{ \}}\\
\end{align*}

(Note that the tail recursion transformation given by $D$ and $T_{\ttt{f}}$ is completely independent of the \ttt{E} type and the transformations associated to the \ttt{E} type. As a result, the tail recursion transformation can be used on its own.)

\begin{align*}
  &C^{*}\expr{\ttt{x}} :=
    \begin{cases}
      \ttt{x} & \text{if \ttt{x} has no marked subexpressions}\\
      C^{*}\expr{C\expr{\ttt{externalize y}}} & \text{if \ttt{externalize y} is the first marked subexpression of \ttt{x}}\\
    \end{cases}\\
\end{align*}
\begin{align*}
  &C\expr{\ttt{externalize (runIter x)}} := \ttt{TailRec $M\expr{\ttt{x}}$}\\
  &C\expr{\ttt{externalize (x + y)}} := \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} := \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &C\expr{\ttt{externalize ($\lambda$x $\rarr$ body)}} := A\expr{\lambda \ttt{x} \rarr \ttt{body}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} := \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} := \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} := \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} := \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} := \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} := \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} :=
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}

@@

\clearpage
\section{Citations and Bibliographies}

\begin{tcolorbox}
  \textbf{TODO}: Fill in
\end{tcolorbox}
